### 2024-11-01 project1/nsSurvey.tex
new

Instead of using a figure, we provide a summary of the empirical convergence results of the MLMC procedure with a decomposition table of the MSEs in Table~\ref{tab1:mlmc-mse}.
The MSEs of the MLMC procedure are decomposed into the bias and the variance of the estimator.
The MSEs of the standard nested simulation procedure with a similar total simulation budget are also provided for comparison.
Since the MLMC procedure is designed with a fixed number of outer simulation paths, the benefit of the MLMC procedure is minimal when the total simulation budget is large.
More specifically, when $\Gamma$ is large, the standard nested simulation procedure with a bootstrap-based budget allocation strategy benefits from having a larger number of outer simulation paths, and the MSE of the standard nested simulation procedure is lower than that of the MLMC procedure with a fixed number of outer simulation paths.

@@

Table~\ref{tab1:complexity} shows the algorithmic complexity of the nested simulation procedures.
For a $d$-dimensional nested estimation problem, the simulation cost for all procedures is $\mathcal{O}(dMN)$.
The simulation cost is omitted from Table~\ref{tab1:complexity}, as all procedures are given the same simulation budget.
Given $M$ outer samples and the corresponding $M$ inner sample averages, the algorithmic complexity of the additional operations does not involve $N$ thus can be written in terms of $M$ only.
The training cost includes the cost of fitting the metamodel and the cost of cross-validation for nonparametric regression metamodels.
For the standard procedure, the training cost is $0$ due to the absence of a metamodel. 
Its prediction cost $\mathcal{O}(M)$ comes from the evaluation of the function $h$ for $M$ samples.

@@

However, it is dependent on the complexity of the payoff function.

@@

The prediction cost of the regression-based procedure is $\mathcal{O}(pM)$, which comes from the multiplication of the design matrix by the estimated coefficients.

@@

During training, a tree is constructed to store the distance, which has complexity $\mathcal{O}(M\log(M))$.
The prediction cost of the kernel smoothing-based procedure is $\mathcal{O}(kM\log(M))$, which comes from a query of the K-D tree for $k$ nearest neighbors for $M$ samples.

@@

For the likelihood ratio-based procedure, the training cost is $0$ as no training is required.
The prediction cost of the likelihood ratio-based procedure is $\mathcal{O}(M^2)$, which comes from the calculation of the likelihood weights for $M$ samples.
For the KRR-based procedure, the main training cost comes from inverting an $M \times M$ kernel matrix~\citep{scholkopf2002learning}, which has complexity $\mathcal{O}(M^3)$ using Gauss-Jordan elimination.

@@

The prediction cost of the KRR-based procedure is $\mathcal{O}(M^2)$, which comes from the multiplication of the kernel matrix by the estimated coefficients.
Among the metamodel-based procedures, regression is the most efficient as $p$ is usually much smaller than $M$. 

>>>>

We provide a summary of the empirical convergence results of the MLMC procedure with a decomposition table of the MSEs in Table~\ref{tab1:mlmc-mse}.
The MSEs of the MLMC procedure are decomposed into the bias and the variance of the estimator.
The MSEs of the standard nested simulation procedure with a similar total simulation budget are also provided for comparison.
Since the MLMC procedure is designed with a fixed number of outer simulation paths, the benefit of the MLMC procedure is minimal when the total simulation budget is large.
More specifically, when $\Gamma$ is large, the standard nested simulation procedure with a bootstrap-based budget allocation strategy benefits from having a larger number of outer simulation paths, and the MSE of the standard nested simulation procedure is lower than that of the MLMC procedure with a fixed number of outer simulation paths.

@@

Table~\ref{tab1:complexity} shows the algorithmic complexity of the nested simulation procedures.
For a $d$-dimensional nested estimation problem, the simulation cost for all procedures is $\mathcal{O}(dMN)$.
The simulation cost is omitted from Table~\ref{tab1:complexity}, as all procedures are given the same simulation budget.
Given $M$ outer samples and the corresponding $M$ inner sample averages, the algorithmic complexity of the additional operations does not involve $N$ thus can be written in terms of $M$ only.
The training cost includes the cost of fitting the metamodel and the cost of cross-validation for nonparametric regression metamodels.

For the standard procedure, 
\begin{itemize}
    \item the training cost is $0$ due to the absence of a metamodel. 
    \item Its prediction cost $\mathcal{O}(M)$ comes from the evaluation of the function $h$ for $M$ samples.
\end{itemize}

@@

\begin{itemize}
    \item The training cost is $\mathcal{O}(p^2M) + \mathcal{O}(p^3)$.

@@

          $p$ is fixed by the basis function, which is selected based on the complexity of the payoff function.
    \item The prediction cost of the regression-based procedure is $\mathcal{O}(pM)$, which comes from the multiplication of the design matrix by the estimated coefficients.
\end{itemize}

@@

\begin{itemize}
    \item During training, a tree is constructed to store the distance, which has complexity $\mathcal{O}(M\log(M))$.
    \item The prediction cost of the kernel smoothing-based procedure is $\mathcal{O}(kM\log(M))$, which comes from a query of the K-D tree for $k$ nearest neighbors for $M$ samples.

@@

\end{itemize}
For the likelihood ratio-based procedure, 
\begin{itemize}
    \item the training cost is $0$ as no training is required.
    \item The prediction cost of the likelihood ratio-based procedure is $\mathcal{O}(M^2)$, which comes from the calculation of the likelihood weights for $M$ samples.
\end{itemize}
For the KRR-based procedure, 
\begin{itemize}
    \item the main training cost comes from inverting an $M \times M$ kernel matrix~\citep{scholkopf2002learning}, which has complexity $\mathcal{O}(M^3)$ using Gauss-Jordan elimination.

@@

    \item The prediction cost of the KRR-based procedure is $\mathcal{O}(M^2)$, which comes from the multiplication of the kernel matrix by the estimated coefficients.
\end{itemize}
Among the metamodel-based procedures, parametric regression is the most efficient.
In regression, the number of features is usually much less than the number of data points, i.e., $p<M$. 
